\documentclass[pagesize,enlargefirstpage=on,fontsize=12pt,juliette]{scrlttr2}

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{polyglossia}

\setlength{\footskip}{0pt}

\setmainfont[Mapping=tex-text]{Gentium Basic}

\KOMAoptions{pagenumber=off,backaddress=false}

\begin{document}


\begin{letter}{Science Park 904 \\ 1098 XH Amsterdam \\ The Netherlands}

    \setkomavar{subject}{Application for International Mobility at the University Of Amsterdam}
    \opening{To whom it may concern,}


    % Introduction

    My name is Juliette Piquard. I am a student at Polytech UPMC, majoring in
    Material Science. I am writing in order to apply for the chemistry master's
    degree at the University of Amsterdam.

    This exchange program offers me the possibility of studying a new field of
    chemistry: the environmental chemistry.  Indeed, the environmental studies and
    sustainable development are fields that have always interested me. Thus,  I
    would like to develop my abilities in chemistry. I find that the offered
    master’s degree matches my professional aspirations that are among others
    analytical sciences. It would be a chance for me to use this knowledge and
    learn more in this field. This would enhance my knowledge and skills in the
    field as I have already obtained a bachelor’s degree in physics and chemistry

    Finally, I am deeply interested by the opportunity given to students which
    allows them to study in a foreign country. The fact that this program is based
    out of the University of Amsterdam interests me as it would allow not only for
    academic pursuits, but cultural discovery as well.  I believe that it would
    provide a rewarding experience in my professional environment in addition to
    helping me grow in my personal development.

    \closing{Thank you for your consideration,}

\end{letter}
\end{document}
